What is happening on Twitter? A framework for student research projects with tweets

### 2020-11-02 Rmd/jse-special-issue-2020-november.Rmd
added requested sentence.

We identified the top ten most probable terms for each of ten topics in our models 
(Figures \@ref(fig:may24), \@ref(fig:may25), \@ref(fig:may26)). 
We plotted the within-topic word probabilities as bar graphs. We see that topic-specific 
word probabilities seldom exceed 0.05. We also note that some words are heavily weighted in 
multiple topics. This observation complicates semantic topic interpretation. We 
also caution that the results display expletives (that appeared on Twitter) and may be "not suitable for work (NSFW)".

```{r, may24, fig.cap = 'Top terms for LDA model from May 24, 2020. Results contain expletives and may be "not suitable for work (NSFW)".'}
knitr::include_graphics("../results/beta-2020-05-24.png")
```

>>>>

We identified the top ten most probable terms for each of ten topics in our models 
(Figures \@ref(fig:may24), \@ref(fig:may25), \@ref(fig:may26)). 
We plotted the within-topic word probabilities as bar graphs. We see that topic-specific 
word probabilities seldom exceed 0.05. We also note that some words are heavily weighted in 
multiple topics. This observation complicates semantic topic interpretation. We 
also caution that the results display expletives (that appeared on Twitter) and may be "not suitable for work (NSFW)". 
Instructors may apply a filter to remove common expletives before LDA modeling of tweets.

```{r, may24, fig.cap = 'Top terms for LDA model from May 24, 2020. Results contain expletives and may be not suitable for work (NSFW).'}
knitr::include_graphics("../results/beta-2020-05-24.png")
```
